---
title: "Introduction to the Quarantine Breach Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the Quarantine Breach Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package contains three datasets related to COVID-19 quarantine breaches in Australia.

## Loading the Data

To get started, load the package. Once loaded, you can access the datasets directly.

```{r, message=FALSE, warning=FALSE}
library(quarantine)
library(ggplot2)
library(dplyr)
```

## The Breaches Dataset

The `breaches_data` tibble contains information on individual breach events.

```{r}
head(breaches_data)
```

## The Cases Summary

The `cases_data` tibble provides a summary of breaches and overseas cases by state.

```{r}
head(cases_data)
```

## Visualization examples

```{r}
#| fig-width: 5
# Breaches by state
breach_summary <- breaches_data %>%
  group_by(state) %>%
  summarise(
    n_breaches = n(),
    n_onward = sum(onward, na.rm = TRUE)
  ) %>%
  arrange(desc(n_breaches))

ggplot(breach_summary, aes(x = reorder(state, -n_breaches), y = n_breaches)) +
  geom_col(fill = "steelblue") +
  labs(title = "Quarantine Breaches by Australian State",
       x = "State", y = "Number of Breaches") +
  theme_minimal()
```
